Data Exploration: IUCN and AquaMaps

### 2016-09-03 clip_depth/coral_maps.Rmd
dammit - need to redo central limit calcs

coral_comp <- coral_cells_iucn %>%
  select(-iucn_sid) %>%
  mutate(deep = deep * 200) %>%
  distinct()

rast_coral_comp <- subs(x = loiczid_raster, y = coral_comp %>% select(loiczid, deep), 
                     by = 'loiczid', which = 'deep', 
                     subsWithNA = TRUE) %>%
  crop(extent(c(-180, 180, -63, 85)))

map_coral_comp <- 
  tm_shape(rast_coral_comp) +
    tm_raster(breaks = c(0, 200, Inf),
              palette = c('lightblue', 'royalblue4'),
              colorNA = NULL,
              title = 'depth (meters)',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            legend.text.size = .35,
            legend.title.size = .45,
            # title.position = 'TOP', 
            legend.outside = FALSE, 
            legend.position = c('left', 'bottom'),
            legend.bg.color = 'white',
            legend.bg.alpha = .5,
            attr.outside = TRUE)

>>>>

coral_comp <- coral_cells_iucn %>%
  dplyr::select(-iucn_sid) %>%
  mutate(deep = deep * 200) %>%
  distinct() %>%
  as.data.frame()

rast_coral_comp <- raster::subs(x = loiczid_raster, y = coral_comp %>% select(loiczid, deep), 
                     by = 'loiczid', which = 'deep', 
                     subsWithNA = TRUE) %>%
  crop(extent(c(-180, 180, -63, 85)))

map_coral_comp <- 
  tm_shape(rast_coral_comp) +
    tm_raster(breaks = c(0, 200, Inf),
              palette = c('lightblue', 'royalblue4'),
              colorNA = NULL,
              title = 'depth (meters)',
              alpha = 1) +
  tm_shape(World) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            legend.text.size = .5,
            legend.title.size = .6,
            # title.position = 'TOP', 
            legend.outside = FALSE, 
            legend.position = c('left', 'bottom'),
            legend.bg.color = 'white',
            legend.bg.alpha = .5,
            attr.outside = TRUE)

### 2016-09-03 clip_fao/fao_clip_pac.Rmd
dammit - need to redo central limit calcs

``` {r central_band}
### 25 S to 5 N  - look for spikes at 120W (240E), 175W (185E), 80E (and 77E)
am_spp_central <- am_spp_latlong %>%
  filter(centerlat <= 5 & centerlat >= -25)

@@

spp_cells_clipped <- read_csv(file.path(dir_git, 'clip_fao', 'spp_cells_clipped_e.csv'))

@@

rast_spp_map_e <- 
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              breaks = c(1, 15, 100, 200, 300, Inf),
              colorNA = 'lightblue1',
              textNA = 'Zero',
              title = 'Species count',
              alpha = 1) +
  tm_shape(World1) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_shape(fao_polys) +
    tm_borders(col = 'grey40', lwd = 0.25) +
    tm_text('F_AREA_1',
            col = 'orangered4',
            fontface = 'bold.italic',
            fontfamily = 'Helvetica',
            size = .35) +
  tm_layout(# basemaps = "Esri.WorldTopoMap", 
            frame = TRUE,
            legend.text.size = .35,
            legend.title.size = .45,
            # title.position = 'TOP', 
            legend.outside = FALSE,
            legend.position = c('right', 'top'),
            legend.bg.color = 'white',
            legend.bg.alpha = .8,
            attr.outside = TRUE)

@@

save_tmap(rast_spp_map_e, 
          file.path(dir_fig, 'map_am_edge_map.png'), 
          width = 19, 
          # height = 6, 
          units = 'cm', dpi = 600)

@@

message('grouping affected species and summing to loiczid')
### group affected spp by loiczid and sum
spp_cells_clipped <- am_spp_cells %>%
  filter(am_sid %in% spp_examples_w$am_sid) %>%
  group_by(loiczid) %>%
  summarize(n_spp = n())

>>>>

``` {r central_band}
### 25 S to 20 N  - look for spikes at 120W (240E), 175W (185E), 80E (and 77E)
am_spp_central <- am_spp_latlong %>%
  filter(centerlat <= 20 & centerlat >= -25)

@@

spp_cells_clipped <- read_csv(file.path(dir_git, 'clip_fao', 'spp_cells_clipped_e.csv')) %>%
  as.data.frame()

@@

### boundary line
fao_boundary <- Line(matrix(c(185, 185, -25, 5), ncol = 2)) %>%
  Lines(ID = 'a') %>%
  list() %>%
  SpatialLines()

rast_spp_map_e <- 
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              breaks = c(1, 15, 100, 200, 300, Inf),
              colorNA = 'lightblue1',
              textNA = 'Zero',
              title = 'Species count',
              alpha = 1) +
  tm_shape(World1) +
    tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
  tm_shape(fao_polys) +
    tm_borders(col = 'grey40', lwd = 0.25) +
    tm_text('F_AREA_1',
            col = 'orangered4',
            fontface = 'bold.italic',
            fontfamily = 'Helvetica',
            size = .5) +
  tm_shape(fao_boundary) +
    tm_lines(col = 'blue', lwd = 1.5) +
  tm_layout(# basemaps = "Esri.WorldTopoMap", 
            frame = TRUE,
            legend.text.size = .5,
            legend.title.size = .6,
            # title.position = 'TOP', 
            legend.outside = FALSE,
            legend.position = c('right', 'top'),
            legend.bg.color = 'white',
            legend.bg.alpha = .9,
            attr.outside = TRUE)

@@

save_tmap(rast_spp_map_e, 
          file.path(dir_fig, 'map_am_edge.png'), 
          width = 19, 
          # height = 6, 
          units = 'cm', dpi = 600)

@@

message('grouping affected species and summing to loiczid')
### group affected spp by loiczid and sum
spp_cells_clipped <- am_spp_cells %>%
  filter(am_sid %in% spp_examples_w$am_sid) %>%
  group_by(loiczid) %>%
  summarize(n_spp = n()) %>%
  as.data.frame()
